Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-08-17 prevalence_testing/postshocktest2022draft.tex
reconciled Quaedvlieg results within the context of the unemployment example

>>>>

\vspace*{0.5cm}\textcolor{red}{A naive test for the presence of a mean-shift shock effect predictably decays very quickly as more and more post-shock data is added for fitting purposes when, in truth, the shock is transient. However, the Quaedvlieg method runs $h = 1,...,H$ ahead forecasts that will not necessarily indicate a quickly decaying shock due to the training data for the model including post-shock responses that have yet to decay. Thus the unadjusted and adjusted forecasts can deviate sharply when their underlying models are fit to a small amount of post-shock data. When $H$ is small, there is a lot of post-shock data under consideration, and the shock decays quickly, the initial shock   may not be detected by the Quaedvlieg method due to a loss-difference matrix evaluating several differences that are negligible far away from the initial shock. The same can be true when $H$ is large. However, for medium size $H$, the influence of fitting the initial post-shock data may not yet accommodate the sharply decayed shock. The result of this is that the Quaedvlieg method can indicate a shifted significant difference between the adjusted and un-adjusted forecasts.  (loss-difference matrix has dimensions $(T - T^* - \max(\lceil1.5\sqrt{T - T^*}\rceil, H))  \times H$) When we have limited sample size, we should not consider large $H$.}
